The first high-redshift changing-look quasars

### 2020-07-07 tex/MNRAS_submission/rv1/reply2referee.txt

(b) In the 6th paragraph (starting with "Details of the atomic transitions...") the authors note some of the lines present in the near-UV spectra of quasars and the ionization energies of the corresponding ions. I am concerned that, as written, this paragraph may be misleading to the non-expert reader and may propagate misconceptions. Most of the strong lines in the near-UV spectrum are collisionally excited (e.g., the C IV 1550 doublet; the He II 1640 recombination line is among the exceptions). Therefore the ionization potential of the C IV ion discussed in this paragraph is much less interesting/relevant than the ionization potential of the C III ion (i.e., the photon energy needed to CREATE the C IV ion). Considering the ions producing strong lines in this spectral region, I would argue that the most noteworthy ionization potential is that of the N IV ion, ~78 eV, since it represents the highest photon energy needed to produce the ions that emit the observed emission lines in the spectral range of interest. Therefore, I would strongly recommend that the authors revise this paragraph to explain the physical significance of the ionization potentials in this particular context more clearly and to simplify the argument they make.

       	  We thank the referee for their very thoughtful notes on this point.
	  We have changed and updated the text with the comments above
	  taken into account.

(c) Table 1: This table is rather long-winded and includes a lot of atomic data that do not seem to be used anywhere in the paper, save for some of the ionization potentials mentioned in the 6th paragraph of section 1 (see my previous comment). I would recommend that this table be removed and any information from this table that is useful be included in the main text. In my opinion, as I argue above, the ionization energy of the N IV ion is the main number of interest to the discussion.

      	  We agree with this comment and to help the reader, in Table 1 we have removed the confusing ``Ionization Potential'' column,
	  while adding a column to the table noting the "Production Mechanism'' of each emission line.
	  We have a strong preference to retain this table, but leave it as a decision to the Editor as to whether to do so.

@@

(iii) Finally, I would suggest noting how many quasars were selected for visual inspection by the automatic algorithm before the three final candidates were identified.

        Text has been added here for additional explanation.

(b) Figure 1. -- I found this figure to be rather busy, packed with information, and difficult to read. I would recommend breaking it up into two separate figures, one including the light curves and one including the spectra. In the process of doing so, I would recommend that the authors write the names of the quasars in the corresponding panels and make the fonts considerably larger so that the labels are easier to read (especially the fonts in the sub-panels that zoom in on specific emission lines).

	 As suggested, we have split the light curve and spectral figures up, increased the size of the fonts,
         and have writen the names of the quasars in the approriate panels.

@@

(b) In the first paragraph of section 3.2 the authors note that they set E(B-V)=0 in the fitting process. Is this the reddening intrinsic to the quasar or does it also include the reddening in the Milky Way? I presume the latter is known and could (and should) be corrected.

       We have updated the results (Table 3) and figures (Figs 5, 6
       and 7) obtained by taking the Milky way extinction values for
       the three objects into account.

(c) Equation (1) in section 3.3. -- This equation, as written, appears to be wrong because the LHS is a log while the RHS is not and there should be constants or calibration factors to connect the black hole mass to the luminosity and FWHM combination. Moreover, the exponent of the luminosity is not exactly 0.5 according to empirical determinations. I would very strongly recommend that the authors correct this equation and revise the relevant discussion. Section 3.7 of the paper by Shen et al. (2011, cited just before equation 1) includes a detailed discussion of the calibration of this relation and several references to the original papers that report the calibration factors. I recommend that the authors begin by consulting that paper and then tracking down the most up-to-date calibration of equation (1), which should be the most appropriate calibration to use here (section 4 of Grier et al. 2019, ApJ, 887, 38 would be a good place to start in order to find the most up-to-date calibrations). The revised text should include appropriate references to the original papers reporting the calibration adopted by the authors.

   	Yes, this is an excellent point. We have updated and corrected the equation
	and revised the relevant discussion, adding key text and references here.

### 2020-07-07 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
tex/MNRAS_submission/rv1 update

Photoionization followed by recombination determines the ionization
level of carbon, and collisional excitation from the ground level of
\civ\ determines the line intensity. Other processes do happen,
(including radiative and three body recombination to the upper level
of the transition), but they are much slower unless the density is
extremely high \citep[e.g., ][and H. Netzer,
priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
($k_{\rm B} T \sim 5 \times10^{5}$ K) can create the triply ionised,
\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
}
%%
Details of the atomic transitions and physical mechanisms that produce
strong rest-frame UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}.

@@

\subsection{Virial Black Hole Masses}
\label{sec:BH_masses} 
The FWHMs of quasar broad lines are related to the mass of the SMBH
powering the quasar phenomenon, and that mass is assumed to be
constant on any human timescale.  Hence it is instructive to check
whether the virial products, which are the basic quantity used to
calculate single-epoch black hole mass estimates, show any
variation.

This approach assumes that the broad-line region (BLR) is
virialized \citep[e.g.][]{Shen2011, Calderone2017}.
{\bf However, the \civ\ line in particular for the broad emission lines is
observed to have
line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, 
very strong blueshifts \citep[as mentioned in the Introduction, see ][]{Richards2011},
and a component of the line profile that does not reverberate \citep[][]{Denney2012}
blurring the picture of the BH mass estimation.
With these key cavaets in mind, we acknowledge the black hole mass estimates
will have a large error, likely $\sim$0.5 dex.
}
The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
  \label{eqn:virial_masses}
\end{equation}
\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

We report a virial product for the \civ\ CLQs in the last column of
Table~\ref{tab:QSFit-results}.  {\bf Since our purpose is to check if
this measurement varies significantly across epochs, here we use
$\gamma=0.5$ as the power-law slope and are not directly concerned
with the offset.
%%
 The quoted uncertainties account only for the propagation of uncertainties in the continuum luminosities and line widths.  However, typical uncertainties associated to single epoch virial mass are $\sim$~0.5 dex, hence} implying that the virial products for our three
high-redshift CLQs are all remarkably constant and compatible with
single black hole masses per source, even in those cases where the
\civ\ estimates were deemed potentially unreliable. The object showing
the largest variation is J2228+2201, with the BH mass estimate spanning a range of 0.66~dex.

{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial masses 
calculated using equation~\ref{eqn:virial_masses}, the measured luminosites
and FWHM from QSFit and the \citet{VestergaardPeterson2006} calibrations.
}
 %%
\citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
masses based on \mgii\ and \civ\ for the SDSS/BOSS observations of our
targets. For J1205+3422, \citet{Shen2011} report $\log (M_{\rm BH,
MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
= 9.49 \pm 0.04$. We use the mean of five values --- three from our
three epochs and two from \citet{Shen2011} --- to calculate an adopted
SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
J1638+2827 also has two virial mass measurements from
\citet{Shen2011}, as well as two measurements from
\citet{Kozlowski2017}. The mean mass measurement adopted for
J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201,
there are two \citet{Kozlowski2017} measurements, leading to a mean
adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these
mean SMBH masses when calculating the Eddington ratios.

>>>>

Photoionization followed by recombination determines the ionization
level of carbon, and collisional excitation from the ions ground level 
determines the line intensity. Other processes do happen,
(including radiative and three body recombination to the upper levels 
of the transition), but they are much slower unless the density is
extremely high \citep[e.g., ][and H. Netzer,
priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply ionised,
\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
}
%%
Details of the atomic transitions and physical mechanisms that produce
strong rest-frame UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}.

@@

\subsection{Virial Black Hole Masses}\label{sec:BH_masses} 
The FWHMs of quasar broad lines are related to the mass of the SMBH
powering the quasar phenomenon, and that mass is assumed to be
constant on any human timescale.  Hence it is instructive to check
whether the virial products, which are the basic quantity used to
calculate single-epoch black hole mass estimates, show any
variation.

This approach assumes that the broad-line region (BLR) is virialized
\citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
Mejia-Restrepo2018}.  {\bf However, the \civ\ line is observed to have
line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
strong blueshifts \citep[as mentioned in the Introduction, see
][]{Richards2011}, and a component of the line profile that does not
reverberate \citep[][]{Denney2012}.  These issues make the virial BH
mass estimate uncertain. \citet{Runnoe2013}, 
\citet{Mejia-Restrepo2016}, \citet{Coatman2017}, 
\citet{Mejia-Restrepo2018} and \citet{Grier2019} all present studies
into improving \civ-based single-epoch black hole mass estimates. With
these cavaets in mind, we acknowledge the BH mass estimates will have
a large error, likely $\sim$0.5 dex. }
The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
  \label{eqn:virial_masses}
\end{equation}
\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

We report a virial product for the \civ\ CLQs in the last column of
Table~\ref{tab:QSFit-results}.  {\bf Since our purpose is to check if
this measurement varies significantly across epochs, here we use
$\gamma=0.5$ as the power-law slope and are not directly concerned
with the offset.  The quoted uncertainties account only for the
propagation of uncertainties in the continuum luminosities and line
widths.  As noted above, with typical uncertainties associated to
single epoch virial mass around $\sim$0.5 dex,} this implies that the
virial products for our three high-redshift CLQs are all remarkably
constant and compatible with single black hole masses per source, even
in those cases where the \civ\ estimates were deemed potentially
unreliable. The object showing the largest variation is J2228+2201,
with the BH mass estimate spanning a range of 0.66~dex.

{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial
masses calculated using equation~\ref{eqn:virial_masses}, the measured
luminosites and FWHM from QSFit and the
\citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
\citet{Kozlowski2017} report virial black hole masses based on \mgii\
and \civ\ for the SDSS/BOSS observations of our targets. For
J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH, MgII}/M_{\odot})
= 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
0.04$.

We use the mean of five values --- three from our three epochs
and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of
$\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.  J1638+2827
also has two virial mass measurements from \citet{Shen2011}, as well
as two measurements from \citet{Kozlowski2017}. The mean mass
measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot}
= 9.09$. For J2228+2201, there are two \citet{Kozlowski2017}
measurements, leading to a mean adopted mass of $\log(M_{\rm BH,
vir}/M_{\odot} = 9.37$. We use these mean SMBH masses when calculating
the Eddington ratios.
